\markboth{BIBLIOGRAFÍA}{BIBLIOGRAFÍA}
\addcontentsline{toc}{chapter}{Bibliografía}


\begin{thebibliography}{99}
    \bibitem{s5pdata} Data Products - Sentinel-5P Mission - Sentinel Online. \textit{Sentinel Online.} [en liña] [sen data] Dispoñible en \textit{\url{ https://sentinels.copernicus.eu/web/sentinel/missions/sentinel-5p/data-products}}.

    \bibitem{erddaphome} ERDDAP - Home Page. \textit{National Centers for Environmental Information (NCEI).} [en liña] [sen data] Dispoñible en \textit{\url{ https://www.ncei.noaa.gov/erddap/index.html}}

    \bibitem{erddapsetup} Set Up Your Own ERDDAP. \textit{ERDDAP.} [en liña] [sen data] Dispoñible en \textit{\url{ https://coastwatch.pfeg.noaa.gov/erddap/download/setup.html}}

    \bibitem{erddapdatasets} Working with the datasets.xml File. \textit{ERDDAP.} [en liña] [sen data] Dispoñible en \textit{\url{ https://coastwatch.pfeg.noaa.gov/erddap/download/setupDatasetsXml.html}}

    \bibitem{ARSETformation} ARSET - High Resolution NO2 Monitoring From Space with TROPOMI. \textit{NASA Applied Sciences.} [en liña] [sen data] Dispoñible en \textit{\url{ https://appliedsciences.nasa
.gov/get-involved/training/english/arset-high-resolution-no2-monitoring-space-tropomi}}

    \bibitem{ARSETtools} ARSET - Data Analysis Tools for High Resolution Air Quality Satellite Datasets \textit{NASA Applied Sciences.} [en liña] [sen data] Dispoñible en \textit{\url{https://appliedsciences.nasa.gov/get-involved/training/english/arset-data-analysis-tools-high-resolution-air-quality-satellite}}

    \bibitem{ARSETaplications} ARSET - Applications of Satellite Observations for Air Quality and Health Exposure \textit{NASA Applied Sciences.} [en liña] [sen data] Dispoñible en \textit{\url{https://appliedsciences.nasa.gov/get-involved/training/english/arset-applications-satellite-observations-air-quality-and-health}}

    \bibitem{S5PL2} Sentinel-5P L2. \textit{Sentinel Hub.} [en liña] [sen data] Dispoñible en \textit{\url{ https://docs.sentinel-hub.com/api/latest/data/sentinel-5p-l2/}}

    \bibitem{s5porbit} S5P Mission. \textit{SentiWiki Home.} [en liña] [sen data] Dispoñible en \textit{\url{https://sentiwiki.copernicus.eu/web/s5p-mission\#TROPOMI-Response-Functions-(Acquisition-Modes)}}

    \bibitem{airpollutants} Types of air pollution. Which pollution is the most dangerous? | Air Quality Monitoring. Monitor in UK \& Europe. Airly Data Platform and Monitors. \textit{Air Quality
    Monitoring. Monitor in UK \& Europe. Airly Data Platform and Monitors | Airly.} [en liña] [sen data] Dispoñible en \textit{\url{https://airly.org/en/the-most-dangerous-types-of-air-pollution/}}

    \bibitem{odata} Documentation - OData. \textit{Copernicus Dataspace} [en liña] [sen data] Dispoñible en: \textit{\url{https://documentation.dataspace.copernicus.eu/APIs/OData.html}}

    \bibitem{copquotas} \textit{Documentation - Quotas and Limitations.} Documentation [en liña] [sen data] Dispoñible en:  \textit{\url{https://documentation.dataspace.copernicus.eu/Quotas.html}}

    \bibitem{HARPdoc} HARP 1.20.2 documentation \textit{HARP manual} [en liña] [sen data] Dispoñible en: \textit{\url{https://stcorp.github.io/harp/doc/html/index.html}}

    \bibitem{HARPCO} S5P\_L2\_CO — HARP 1.20.2 documentation. \textit{HARP manual} [en liña] [sen data] Dispoñible en: \textit{\url{https://stcorp.github.io/harp/doc/html/ingestions/S5P_L2_CO.html}}

    \bibitem{HARPNO2} S5P\_L2\_NO2 — HARP 1.20.2 documentation. \textit{HARP manual} [en liña] [sen data] Dispoñible en: \textit{\url{https://stcorp.github.io/harp/doc/html/ingestions/S5P_L2_NO2.html}}

    \bibitem{HARPO3} S5P\_L2\_O3 — HARP 1.20.2 documentation. \textit{HARP manual} [en liña] [sen data] Dispoñible en: \textit{\url{https://stcorp.github.io/harp/doc/html/ingestions/S5P_L2_O3.html}}

    \bibitem{HARPSO2} S5P\_L2\_SO2 — HARP 1.20.2 documentation. \textit{HARP manual} ([en liña] [sen data] Dispoñible en: \textit{\url{https://stcorp.github.io/harp/doc/html/ingestions/S5P_L2_SO2.html}}

    \bibitem{COmanual} Sentinel-5P TROPOMI Level 2 Product User Manual - Carbon Monoxide. \textit{Sentinel Online} [en liña] [sen data] Dispoñible en: \textit{\url{https://sentinels.copernicus.eu/web/sentinel/user-guides/sentinel-5p-tropomi/document-library/-/asset_publisher/w9Mnd6VPjXlc/content/sentinel-5p-tropomi-level-2-product-user-manual-carbon-monoxide}}

    \bibitem{NO2manual} Sentinel-5P TROPOMI Level-2 Product User Manual - Nitrogen Dioxide. \textit{Sentinel Online} [en liña] [sen data] Dispoñible en: \textit{\url{https://sentinels.copernicus.eu/web/sentinel/user-guides/sentinel-5p-tropomi/document-library/-/asset_publisher/w9Mnd6VPjXlc/content/sentinel-5p-tropomi-level-2-product-user-manual-nitrogen-dioxide}}

    \bibitem{O3manual} Sentinel-5P TROPOMI Level 2 Product User Manual - Ozone Total Column. \textit{Sentinel Online} [en liña] [sen data] Dispoñible en: \textit{\url{https://sentinels.copernicus.eu/web/sentinel/user-guides/sentinel-5p-tropomi/document-library/-/asset_publisher/w9Mnd6VPjXlc/content/sentinel-5p-tropomi-level-2-product-user-manual-ozone-total-column}}

    \bibitem{SO2manual} Sentinel-5P TROPOMI Level 2 Product User Manual - Sulphur Dioxide SO2. \textit{Sentinel Online} [en liña] [sen data] Dispoñible en: \textit{\url{https://sentinels.copernicus.eu/web/sentinel/user-guides/sentinel-5p-tropomi/document-library/-/asset_publisher/w9Mnd6VPjXlc/content/sentinel-5p-tropomi-level-2-product-user-manual-sulphur-dioxide-so2}}

    %\bibitem{} \textit{} [en liña] [sen data] Dispoñible en: \textit{\url{}}

    %\bibitem{} \textit{} [en liña] [sen data] Dispoñible en: \textit{\url{}}

    %\bibitem{} \textit{} [en liña] [sen data] Dispoñible en: \textit{\url{}}

    %\bibitem{} \textit{} [en liña] [sen data] Dispoñible en: \textit{\url{}}

\end{thebibliography}

